Practical Optional Types for Clojure

### 2015-02-21 formal-model.tex
add map value metavariable. compact rules

Types include the top type, untagged unions, functions, singleton types
and class instances. We abbreviate \EmptyUnion{} as \Bot{}, \Value{\Nil{}} as \Nil{} and similarly
for \True and \False.
Function types contain \emph{latent} propositions and object, which, along with the return type,
may refer to the parameter identifier. They are latent because they are instantiated with the
actual object of the argument in applications before they are used in the proposition environment.

@@

\begin{figure*}
  \footnotesize
$$
\begin{altgrammar}
  \expd{}, \e{} &::=& \x{}
                      \alt \v{} 
                      \alt {\comb {\e{}} {\e{}}} 
                      \alt {\abs {\x{}} {\t{}} {\e{}}}
                      \alt {\ifexp {\e{}} {\e{}} {\e{}}}
                      \alt {\trdiff{\doexp {\e{}} {\e{}}}}
                      \alt {\letexp {\x{}} {\e{}} {\e{}}}
                      \alt {\errorvalv{}}
                &\mbox{Expressions} \\
  \v{} &::=&          \true{} \alt \false{} \alt \trdiff{\nil{}}
                      \alt \trdiff{\class{}}
                      \alt \k{}
                      \alt {\const{}}
                      \alt {\closure {\openv{}} {\abs {\x{}} {\t{}} {\e{}}}}
                &\mbox{Values} \\
  {\const{}}           &::=& \classconst \alt \throwconst

@@

    {\TDo}

    {\TClass}

    {\TIf}

    {\TLet}

    {\TKw}

@@

    {\TError}

@@

\begin{figure}
  \footnotesize
  \getmethodfigure{}
  \begin{mathpar}
    \BDefMulti{}

    \BDefMethod{}

    \BBetaMulti{}
  \end{mathpar}
  \caption{Multimethod semantics}
  \label{main:figure:mmsemantics}
\end{figure}

@@

\begin{figure}
  \footnotesize
  \begin{mathpar}
    {\BAssoc}

    {\BGet}

    {\BGetMissing}
  \end{mathpar}
  \caption{HMap Semantics}
  \label{main:figure:hmapsem}
\end{figure}

@@

\getliteral{} and \assocliteral{} lookup and extend immutable maps respectively.
To simplify presentation, we only allow the empty map literal and
restrict lookup and extension to keyword keys. The runtime value of maps {\curlymapvaloverright{\k{}}{\v{}}}
is not part of the language syntax.

@@

    \BMethod{}

    \BNew{}
  \end{mathpar}
  \caption{Java Interoperability Semantics}
\end{figure}

\begin{figure}
  \footnotesize
  \begin{mathpar}
    {\TNewStatic}

    {\TFieldStatic}

>>>>

Types include the top type, untagged unions, functions, singleton types
and class instances. We abbreviate \EmptyUnion{} as \Bot{}, {\ValueNil} as \Nil{} and similarly
for \True and \False.
Function types contain \emph{latent} propositions and object, which, along with the return type,
may refer to the parameter identifier. They are latent because they are instantiated with the
actual object of the argument in applications before they are used in the proposition environment.

@@

\begin{figure*}
  \footnotesize
$$
\begin{altgrammar}
  \expd{}, \e{} &::=& \x{}
                      \alt \v{} 
                      \alt {\comb {\e{}} {\e{}}} 
                      \alt {\abs {\x{}} {\t{}} {\e{}}}
                      \alt {\ifexp {\e{}} {\e{}} {\e{}}}
                      \alt {\trdiff{\doexp {\e{}} {\e{}}}}
                      \alt {\letexp {\x{}} {\e{}} {\e{}}}
                      %\alt {\errorvalv{}}
                &\mbox{Expressions} \\
  \v{} &::=&          \singletonmeta{}
                      \alt {\const{}}
                      \alt {\closure {\openv{}} {\abs {\x{}} {\t{}} {\e{}}}}
                &\mbox{Values} \\
  {\const{}}           &::=& \classconst \alt \throwconst

@@

    {\TDo}
    %{\TClass}
    {\TIf}
    {\TLet}

    %{\TKw}

@@

    %{\TError}

@@

\begin{figure}
  \footnotesize
  \getmethodfigure{}
  \begin{mathpar}
    \BDefMulti{}
    \BBetaMulti{}

    \BDefMethod{}
  \end{mathpar}
  \caption{Multimethod semantics}
  \label{main:figure:mmsemantics}
\end{figure}

@@

\begin{figure}
  \footnotesize
  \begin{mathpar}
    {\BAssoc}
    {\BGet}
    {\BGetMissing}
  \end{mathpar}
  \caption{HMap Semantics}
  \label{main:figure:hmapsem}
\end{figure}

@@

\getliteral{} and \assocliteral{} lookup and extend immutable maps respectively.
To simplify presentation, we only allow the empty map literal and
restrict lookup and extension to keyword keys. The metavariable \mapval{}
ranges over the runtime value of maps {\curlymapvaloverright{\k{}}{\v{}}}.

@@

    \BNew{}

    \BMethod{}
  \end{mathpar}
  \caption{Java Interoperability Semantics}
\end{figure}

\begin{figure}
  \footnotesize
  \begin{mathpar}
    {\TNewStatic}
    {\TFieldStatic}
